Reproducible Builds for\\ Computational Research Papers

### 2020-09-20 ms.tex
{make test}

The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
The \textit{author} only needs to edit (or use the `touch' UNIX utility to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.

@@

Regarding \LaTeX\ a common culprit against reproducibility is the time-date metadata embedded in the pdf output.
These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\end{lstlisting}

>>>>

The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
The \textit{author} only needs to edit (or use the `touch' UNIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.

@@

We split to train, validation and test datasets and compare the use of ReLU and SELU activation functions in a VGG11 model.
The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.
Regarding \LaTeX\ a common culprit against reproducibility is the time-date metadata embedded in the pdf output.
These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\end{lstlisting}
